### 2020-06-09 text/article_vedrovice.Rmd
continue analysis spatial analysis

```{r init, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
```

@@

Data is analyzed in an R environment for statistical computing and graphics
[@rcore]  using functions of readr [@wickham2017a], dplyr [@wickham2016] and
reshape2 [@wickham2007] packages to manipulate the data.
Function daisy [@kaufman1990] from package cluster [@maechler2016] is used to
count distances between observations used in further analyses.
<!-- ADD METHODS AND PACKAGES USED IN R -->

@@

@@

```{r vtable}
vstat <- read_csv(here::here("data/temp", "v_statistics.csv")) %>% 
    select(full, v, p) %>% 
    mutate(v = round(v, 2), p = round(p, 2)) %>% 
    rename("variable" = full, "v statistic" = v, "p value" = p)

@@

>>>>

```{r init, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
library(here)
```

@@

Data is analyzed in an R environment for statistical computing and graphics
[@rcore]  using functions of readr [@wickham2017a], dplyr [@wickham2016] and
reshape2 [@wickham2007] packages to manipulate the data.
Function daisy [@kaufman1990] from package cluster [@maechler2016] is used to
count distances between observations used in further analyses.
<!-- ADD METHODS AND PACKAGES USED IN R, or into SI?-->

## Spatial randomness

@@

With $n = 999$ permutations of the original data matrix the results obtained
are robust

@@

By counting co-occurences of analyzed variables on simulated data matrices and comparing
the distributions of the two studied statistics with the values calculated for
the original dataset we can establish whether the overall pattern of artefacts
distribution in the graves is non-random and further identify artefacts that deviate
from the random pattern.
The value of $S$ statistic is deemed significantly large at the 0.05 alpha level with
$S \approx 14 $ and $ p \approx $ (Fig. \@ref(fig:f-sstat)).
This suggests that there is enough evidence that the overall distribution of
artefacts in the graves is not random.

```{r t-vstat}
vstat <- read_csv(here("data/temp", "v_statistics.csv")) %>%
    select(full, v, p) %>%
    mutate(v = round(v, 2), p = round(p, 2)) %>%
    rename("variable" = full, "v statistic" = v, "p value" = p)

@@

```{r f-sstat, fig.cap = "Distribution of simulated and observed S statistic"}
knitr::include_graphics(here("plots", "s_statistic.pdf"))
```

```{r f-vstat, fig.cap = "Simulated and observed v statistics for different variables"}
knitr::include_graphics(here("plots", "v_values.pdf"))
```

```{r f-cooc, fig.cap = "Networks of variables frequently present together and exluding each other"}
knitr::include_graphics(here("plots", "cooc_networks.pdf"))
```
